Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
merge

- **Recency Weight**: Applied through an exponential decay function, `exp(-recency * 0.1)`, where "recency" represents the days since the poll was conducted. This ensures that more recent data carries more weight, while older polls have reduced influence.

@@

```{r}
modelsummary::msummary(list(
  "Harris Unweighted" = harris_unweighted_model, 
  "Harris Weighted" = harris_weighted_model,
  "Trump Unweighted" = trump_unweighted_model,
  "Trump Weighted" = trump_weighted_model))

@@

This appendix provides a comprehensive overview of the methodology
employed by the Siena College Polling Institute in conducting its
surveys.Siena College is renowned for its methodologically rigorous
approach to political polling, focusing on accurately capturing voter
sentiment during elections. Siena College has conducted polls in three
key states: Michigan, Wisconsin, and Ohio.

In this section, we will delve into the key components of Siena's
polling methodology, including the target population, sampling frame,
recruitment processes, and the sampling strategies used. We will also
address how non-response is managed and evaluate the strengths and
weaknesses of the questionnaire design. By exploring these elements,
this appendix aims to clarify how Siena College ensures the reliability
and validity of its polling results, contributing valuable insights to
the understanding of voter behavior and election outcomes.

@@

This appendix details the methodology and design for conducting a U.S.
presidential election forecast survey with a budget of \$100,000. The
objective is to generate an accurate and reliable prediction of the
election outcome while ensuring data quality through meticulous
sampling, recruitment, validation, and aggregation of results.\

@@

Our target population is all U.S. citizens eligible to vote in the 2024
U.S. presidential election (age\>=18).

@@

Mitigating Response Order Bias: For nominal questions, we randomize
response options, and for ordinal questions, we vary the order.
Open-ended formats and pauses (e.g., "Who would you vote for? \[pause\]
Candidate A or Candidate B?") further minimize order effects.

@@

Budget Breakdown With a total budget of \$100,000, the allocation for
various components of the survey implementation and data collection is
as follows:

Survey Design and Development: \$2,000 Covers question formatting,
testing, and online integration (e.g., Qualtrics) to ensure
user-friendly and relevant survey design.

Online Panel Providers (Qualtrics, YouGov): \$80,000 200 respondents
recruited at \$400 each, leveraging verified voter panels for
high-quality data.

Social Media Recruitment (Facebook, Instagram): \$12,000 400 respondents
recruited via targeted ads (\$30 each). Anticipating a 50% invalid rate,
allowing for 200 valid responses after validation.

Data Validation and Quality Control: \$6,000 Includes voter registration
checks, attention filters, and post-collection quality review,
especially for social media responses, to ensure data integrity.

>>>>

- **Recency Weight**: Applied through an exponential decay function, exp(-recency * 0.1), where "recency" represents the days since the poll was conducted. This ensures that more recent data carries more weight, while older polls have reduced influence.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| tbl-colwidths: [45,15]
#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
#| layout-ncol: 2
#| label: tbl-summary
modelsummary::msummary(
  list(
    "Harris Unweighted" = harris_unweighted_model, 
    "Harris Weighted" = harris_weighted_model,
    "Trump Unweighted" = trump_unweighted_model,
    "Trump Weighted" = trump_weighted_model
  ))
```

@@

This appendix outlines the methodology used by the Siena College Polling Institute for conducting its surveys. Known for its methodological rigor, Siena College focuses on accurately capturing voter sentiment during elections and has conducted polls in key states such as Michigan, Wisconsin, and Ohio.

In this section, we examine the main components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and sampling strategies. Additionally, we discuss how Siena addresses non-response and review the strengths and weaknesses of its questionnaire design. By detailing these elements, this appendix clarifies how Siena College ensures the reliability and validity of its polling results, offering valuable insights into voter behavior and election dynamics.

@@

This appendix details the methodology and design for conducting a U.S.
presidential election forecast survey with a budget of $\$100,000$. The
objective is to generate an accurate and reliable prediction of the
election outcome while ensuring data quality through meticulous
sampling, recruitment, validation, and aggregation of results.\

@@

Our target population is all U.S. citizens eligible to vote in the 2024
U.S. presidential election (age>=18).

@@

Mitigating Response Order Bias: For nominal questions, we randomize
response options, and for ordinal questions, we vary the order.
Open-ended formats and pauses (e.g., "Who would you vote for? [pause]
Candidate A or Candidate B?") further minimize order effects.

@@

Budget Breakdown With a total budget of $\$100,000$, the allocation for
various components of the survey implementation and data collection is
as follows:

Survey Design and Development: $\$2,000$ Covers question formatting,
testing, and online integration (e.g., Qualtrics) to ensure
user-friendly and relevant survey design.

Online Panel Providers (Qualtrics, YouGov): $\$80,000$ 200 respondents
recruited at $\$400$ each, leveraging verified voter panels for
high-quality data.

Social Media Recruitment (Facebook, Instagram): $\$12,000$ 400 respondents
recruited via targeted ads ($\$30$ each). Anticipating a 50% invalid rate,
allowing for 200 valid responses after validation.

Data Validation and Quality Control: $\$6,000$ Includes voter registration
checks, attention filters, and post-collection quality review,
especially for social media responses, to ensure data integrity.
